---
title: "Debugging R"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bug 1 - Could not find function "ggplot"

```{r, error=TRUE}

# load libraries ----

library(palmerpenguins) # loaded for penguins data

# visualise data ----

ggplot(data = penguins, 
       mapping = aes(x = bill_length_mm, 
                     y = bill_depth_mm)) +
  geom_point()

```

## Follow these steps

- Step 1: Stay calm
- Step 2: Read the error message carefully and look out for helpful advice
- Step 3: If the advice was not helpful, use a search engine of your choice and type:

> "could not find function "ggplot" error R tidyverse"

## Possible issues

You have two possible issues here:

1. The function you have called doesn't exist (you have made a spelling mistake)
2. The R package that contains the function is not loaded

## Solution

In this case, you are facing the second issue. The R Package that contains the function `ggplot()` is not loaded. The function is part of the `{ggplot2}` Package. To load it, write `library(ggplot2)` into your script before you execute the function `ggplot()` is not loaded 

```{r}

# load libraries ----

library(palmerpenguins)
library(ggplot2)

# visualise data ----

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point()

```

# Bug 1 - There is no package called ‘skimr’

```{r}

library(skimr)

```

## Follow these steps

- Step 1: Stay calm
- Step 2: Read the error message carefully and look out for helpful advice
- Step 3: If the advice was not helpful, use a search engine of your choice and type:

> "Error in library(skimr) : there is no package called ‘skimr’"

## Possible issues

1. The R package you have called doesn't exist (you have made a spelling mistake)
2. The R package is not installed

## Solution

In this case, you are facing the second issue. The R Package `{skimr}` is not installed. To install it, call `install.packages("skimr")` in your **Console**. Do this in your Console because you only need to install it once. After you have installed it, call it with `library(skimr)` 

```{r}

# load libraries ----

library(skimr)
library(palmerpenguins)

# explore data ----

skim(penguins)

```

